---
output: github_document
---

<!-- index.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# embrs

<!-- badges: start -->
<!-- badges: end -->

> __embrs__ is in development

__embrs__ was initially written as part of work on a scoping exercise to provide 
early estimates of the environmental impacts of the diesel to electric bus. 

## code sources

__embrs__ code sources: https://github.com/karlropkins/embrs


## Installation

You can install the development version of embrs from [GitHub](https://github.com/) with:

```{r, eval=FALSE}
# install.packages("devtools")
devtools::install_github("karlropkins/embrs")
```

## Example

__embrs__ uses vehicle and route objects to build small-scale emission inventories:

```{r example}
library(embrs)
# some buses
# a ICE diesel bus weighing 15925 kg
bus.1 <- bus_ice(name="E6DV", veh.wt=15925) 
# a battery electric bus weighing 17725 kg (and conventional brakes) 
bus.2 <- bus_bev(name="BEV", veh.wt=17725) 
# like bus.2 but with regenerative brakes operating at 25% efficiency
bus.3 <- bus_bev(name="BEV\nlow", veh.wt=17725, brk.regen = 0.25) 
# like bus.3 but 75% efficiency
bus.4 <- bus_bev(name="BEV\nhi", veh.wt=17725, brk.regen = 0.75)  
# a small fleet
fleet <- bus.1 + bus.2 + bus.3 + bus.4
# some routes 
routes <- route_naei_urban() + route_naei_rural() + route_naei_motorway()
# an inventory
inventory <- fleet * routes
plot(inventory)
```

## Contributing

Contributions are very welcome. Please see both [contribution guidance](https://karlropkins.github.io/embrs/CONTRIBUTING.html) and [code of conduct](https://karlropkins.github.io/embrs/CODE_OF_CONDUCT.html) if interested in contributing.

## License

[GPL-3](https://karlropkins.github.io/embrs/LICENSE.html)
